---
title: "What the package does"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{What the package does}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(MATH4753humm0010)


```


# Introduction

This is a package that contains many functions that arre useful for the course, MATH4753 at the University of Oklahoma. They due a range of different things such as making sophisticated plots. 

# myboot2

This function creates a histogram with a confidence interval and point estimate shown on the graph.

```{r}
myboot2(x = phis$INTTIME )
```


# mycltp

This function creates a histogram of the means of the sample iterations.

```{r}



par(mar=c(1,1,1,1))

mycltp(n=2, iter=1000,lambda=4)

```




# mymlnorm

This function produces a graph of the mean and the standard deviation of a set of data.

```{r}
mymlnorm(x=c(10,12,13,15,12,11,10),mu=seq(5,15,length=1000),sig=seq(0.1,4,length=1000),lwd=2,labcex=1)
```


# myddt

This function creates a plot, csv file, data, and table for the data set and variable entered. 


myddt <- function(df, SPECIES)
{

  WEIGHT <- LENGTH <- RIVER <- NULL

  newdf <- df %>% filter(SPECIES == {{SPECIES}})

  g = ggplot(newdf, aes(x = WEIGHT, y = LENGTH)) + geom_point(aes(col=RIVER)) +
    geom_smooth(formula = y~x +I(x^2), method = "lm") + ggtitle("Audrey Hummell")

  print(g)

  write.csv(x = newdf,
            file = paste0("LvsWfor", SPECIES, ".csv" ),
            row.names = FALSE
            )

  list = list(df = df, newdf = newdf, tab = table(df$RIVER)/length(df$RIVER))

  return(list)

}

